### 2022-10-20 supp/03-gm.botjar.Rmd
<edit index>

# boxplot of vessel centroid size by type
csz.type <- ggplot(qdata, aes(x = type, y = csz, color = type)) + 
  geom_boxplot(notch = FALSE) +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.3) +
  scale_colour_manual(values = wes_palette("Moonrise2")) +
  theme(legend.position = "none") +
  labs(x = 'Group', y = 'Centroid Size')

>>>>

# boxplot of vessel centroid size by type
csz.type <- ggplot(qdata, aes(x = type, y = csz, color = type)) + 
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.3) +
  scale_colour_manual(values = wes_palette("Moonrise2")) +
  theme(legend.position = "none") +
  labs(x = 'Group', y = 'Centroid Size')

### 2022-10-20 supp/index.Rmd
<edit index>

**Neck morphology**:

 * Bottle and jar necks **differ significantly** in shape
 * Bottle and jar necks do not differ in size

```{r pca.warp.ne.index, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Results of PCA summarising shape variation in bottle necks, gray; and jar necks, orange; with shapes + warp grids for maxima/minima of each axis."}
# pca warp neck                   
knitr::include_graphics('images/pca-warp-neck.jpg')
```
```{r botjarneck, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Mean shapes for bottle necks (a), jar necks (b), and comparison of bottle (gray) and jar (black) neck shapes (c)."}
knitr::include_graphics('images/mshape-neck.png')
```

**Basal morphology**:

 * Bottle and jar bases **differ significantly** in shape
 * Bottle and jar bases do not differ in size

```{r pca.warp.ba.index, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Results of PCA summarising shape variation in bottle bases, gray; and jar bases, orange; with shapes + warp grids for maxima/minima of each axis."}
# pca warp                   
knitr::include_graphics('images/pca-warp-base.jpg')
```
```{r botjarbase.index, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Mean shapes for bottle bases (a), jar bases (b), and comparison of bottle (gray) and jar (black) base shapes (c)."}
knitr::include_graphics('images/mshape-base.png')
```

@@

This volume is written in _Markdown_, and all files needed to reproduce it are included in the [GitHub repository](https://github.com/aksel-blaise/aahc-anthro-zoo), which is digitally curated on the Open Science Framework. The reproducible nature of this undertaking provides a means for others to critically assess and evaluate the various analytical components [@RN20915;@RN20916;@RN20917], which is a necessary requirement for the production of reliable knowledge.

@@

The data and analysis code associated with this project can be accessed through this document or the [GitHub](https://seldenlab.github.io/anthro.zoo/) repository, and is digitally curated on the Open Science Framework ([DOI 10.17605/OSF.IO/VZHJR](https://osf.io/vzhjr/)).

>>>>

**Neck/rim morphology**:

 * Bottle and jar neck/rim shapes **differ significantly**
 * Bottle and jar neck/rim sizes do not differ

```{r pca.warp.ne.index, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Results of PCA summarising shape variation in bottle necks/rims, gray; and jar necks/rims, orange; with shapes + warp grids for maxima/minima of each axis."}
# pca warp neck                   
knitr::include_graphics('images/pca-warp-neck.jpg')
```
```{r botjarneck, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Mean shapes for bottle necks/rims (a), jar necks/rims (b), and comparison of bottle (gray) and jar (black) neck/rim shapes (c)."}
knitr::include_graphics('images/mshape-neck.png')
```

**Body/Base morphology**:

 * Bottle and jar body/base shapes do not differ
 * Bottle and jar body/base sizes do not differ

@@

All data and analysis code associated with this project can be accessed through this document or the [GitHub](https://seldenlab.github.io/anthro.zoo/) repository, which is digitally curated on the Open Science Framework ([DOI 10.17605/OSF.IO/VZHJR](https://osf.io/vzhjr/)). The reproducible nature of this undertaking provides a means for others to critically assess and evaluate the various analyses [@RN20915;@RN20916;@RN20917], which is a necessary requirement for the production of reliable knowledge.

@@

### 2022-10-20 tinker/06-gm.base.Rmd
<edit index>

# 3DGM: Body morphology

@@

```{r load.data.ba, echo = TRUE}
# load packages
#devtools::install_github("mlcollyer/RRPP")
#devtools::install_github("geomorphR/geomorph", ref = "Stable", build_vignettes = TRUE)
library(here)
library(geomorph)
library(tidyverse)
library(wesanderson)

@@

```{r pca.warp.ba, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Results of PCA summarising shape variation in the aggregated sample; gray, north-formative/early; orange, north-late/historic; brown, south-formative/early; and black, south-late/historic; with mean shapes (gray) contrasted with max/min shapes (black)."}
# pca warp                   
#knitr::include_graphics('images/pca-warp.jpg')
```

## Body size and shape

@@

```{r def.mod.1.ba, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# body size as a function of vessel form (bottle/jar)?
fit.size.type <- procD.lm(size ~ type,
                            data = gdf,
                            print.progress = FALSE,
                            iter = 9999)

# Procrustes ANOVA: do body sizes differ as a function of vessel form?
anova(fit.size.type)

# body shape as a function of vessel form?
fit.shape.type <- procD.lm(shape ~ type,
                data = gdf,
                print.progress = FALSE,
                iter = 9999)

# Procrustes ANOVA: do body shapes differ as a function of vessel form?
anova(fit.shape.type)
```

@@

```{r mshape.ba, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# subset landmark coordinates to produce mean shapes
new.coords<-coords.subset(A = Y.gpa$coords,
                          group = qdata$type)
names(new.coords)

@@

#knitr::include_graphics('images/mshape-base.png')
```

>>>>

# 3DGM: Base morphology

@@

```{r load.data.ba, echo = TRUE}
# load packages
library(here)
library(geomorph)
library(tidyverse)
library(wesanderson)

@@

### Minima/maxima of PC1/2 with warp grids

```{r min.max.base, echo=TRUE, out.width = "100%", dpi = 300, warning=FALSE}
# plot x/y maxima/minima
## x - minima
ref <- mean.shape <- mshape(Y.gpa$coords)
plotRefToTarget(M1 = ref, 
                M2 = pca$shapes$shapes.comp1$min, 
                method = "TPS")

plotRefToTarget(M1 = ref, 
                M2 = pca$shapes$shapes.comp1$max, 
                method = "TPS")

plotRefToTarget(M1 = ref, 
                M2 = pca$shapes$shapes.comp2$min, 
                method = "TPS")

plotRefToTarget(M1 = ref, 
                M2 = pca$shapes$shapes.comp2$max,
                method = "TPS")
```

```{r pca.warp.ba, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Results of PCA summarising shape variation in bottles, gray; and jars, orange; with shapes + warp grids for maxima/minima of each axis."}
# pca warp                   
knitr::include_graphics('images/pca-warp-base.jpg')
```

## Base size and shape

@@

```{r def.mod.1.ba, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# base size as a function of vessel form (bottle/jar)?
fit.size.type <- procD.lm(size ~ type,
                            data = gdf,
                            print.progress = FALSE,
                            iter = 9999)

# Procrustes ANOVA: do basal sizes differ as a function of vessel form?
anova(fit.size.type)

# base shape as a function of vessel form?
fit.shape.type <- procD.lm(shape ~ type,
                data = gdf,
                print.progress = FALSE,
                iter = 9999)

# Procrustes ANOVA: do basal shapes differ as a function of vessel form?
anova(fit.shape.type)
```

@@

```{r mshape.ba, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE, fig.cap="Mean shapes for bottle bases (a), jar bases (b), and comparison of bottle (gray) and jar (black) base shapes (c)."}
# subset landmark coordinates to produce mean shapes
new.coords<-coords.subset(A = Y.gpa$coords,
                          group = qdata$type)
names(new.coords)

@@

knitr::include_graphics('images/mshape-base.png')
```
